### 2021-03-02 doc/manuscript/Dow_manuscript_Nature.Rmd
Update Dow_manuscript_Nature.Rmd

@@

7. Center for Tropical Forest Science-Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama

@@

>>>>

*Grant Harley (ASSUMING WE USE SMOKIES TREE RING RECORDS)*

@@

7. Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama

@@

The tree-ring records from our focal sites were complemented with a much larger collection spanning **#** deciduous and mixed forest sites in Eastern North America.
Again, species were limited to broadleaf deciduous species with clearly defined xylem porosity (i.e., excluding semi-ring porous).
